Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-10-15 exp1/present2013.tex
introduce style Martin uses
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@675 43ef1190-90fd-4dd7-a769-d0121f02b80e
small changes
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@676 43ef1190-90fd-4dd7-a769-d0121f02b80e
More math
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@677 43ef1190-90fd-4dd7-a769-d0121f02b80e

%\documentclass[english,aspectratio=196]]{ifislide}
%\documentclass[english,print,aspectratio=169]{ifislide}
\documentclass[english,handout,aspectratio=169]{ifislide}
\usepackage{verbatim}

@@

\newcommand{\typed}{\char`\^\char`\^}
\newcommand{\blank}{\char`\_}

\newcommand{\tuple}[1]{\left<#1\right>}
\newcommand{\inter}{\mathcal{I}}
\newcommand{\domain}{\mathop{\mathsf{dom}}}
\newcommand{\range}{\mathop{\mathsf{rg}}}

\LectureDate{24.10.2013}

@@

\title[DoE in SPARQL Evaluations]{Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation}
\subtitle{}
\author{Kjetil Kjernsmo and John Tyssedal}
\maketitle

@@

  \begin{itemize}
  \item Pioneered by Fischer in the 1920s.
  \item Well-established in many fields of engineering, agriculture,
    medicine.
  \item Well-suited to manage very complex experiments.
  \item Requires parameterization of experiments.
  \end{itemize}
\end{frame}
\note{How many is familiar with DoE?}

@@

@@

\begin{block}{Examples}
  \begin{itemize}
  \item A concrete implementation
  \item Hardware platform
  \item Data heterogeneity
  \item Number of triples in the store
  \item Absence or presence of certain language features
  \item Order of experiments
  \item Tuning parameters
  \item Concurrency
  \end{itemize}
\end{block}

@@

  \begin{itemize}
  \item Code and instructions at Github:
    \url{https://github.com/kjetilk/doe-sparql}.
  \item Happy to help getting it to run!
  \end{itemize}

>>>>

%\documentclass[english,aspectratio=196]]{ifislide}
%\documentclass[english,print,aspectratio=169]{ifislide}
%\documentclass[english,handout,aspectratio=169]{ifislide}
\documentclass[english,usenames,dvipsnames,aspectratio=169]{beamer}
\usepackage{verbatim}
\usepackage{config}

\usetheme{ifi_en}

@@

@@

\title[DoE in SPARQL Evaluations]{Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation}
\subtitle{}
\author{Kjetil Kjernsmo and John Tyssedal}
\date{24.10.2013}
\maketitle

@@

  \begin{itemize}
  \item Pioneered by Fischer in the 1920s.
  \item Well-established in many fields of engineering, agriculture,
    medicine.
  \item Well-suited to manage very complex experiments.
  \item Requires parameterization of experiments.
  \end{itemize}
\end{frame}
\note{

  \begin{itemize}
  \item There are problems, but time doesn't allow discussion, more in paper.
  \item How many are familiar with DoE?
  \end{itemize}
}

@@

    \begin{block}{For the mathematically inclined}
      The response variable is a stochastic variable $R$
    \end{block}

@@

\begin{block}{Examples}
  \begin{itemize}
  \item Which concrete implementation
  \item Which Hardware platform
  \item Number of triples in the store
  \item Absence or presence of certain language features
  \item Order of experiments
  \item Level of concurrency
  \end{itemize}
\end{block}

\begin{block}{For the mathematically inclined}
  The response variable is itself a function $R \( a, b, c, \ldots
  \)$, where $a$, $b$, $c$ are factors.
\end{block}

@@

  \begin{itemize}
  \item Code and instructions at Github:
    \url{https://github.com/kjetilk/doe-sparql}.
  \item Happy to help getting it to run!
  \item Happy to discuss collaborations or workshops on this topic!
  \end{itemize}
